### 2020-04-30 README.Rmd
tweaking; fix a typo in referenceing a figure; render only to markdown

```{r apprise-figure, dev = "png", fig.height = 6, fig.width = 7}
appraise(m)
```

@@

    ![Estimated smooths from a GAM](man/figures/README-draw-gam-figure.png)

@@

    ![Model diagnostics figure](man/figures/README-appraise-figure.png)

>>>>

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 7}
appraise(m)
```

@@

    ![Estimated smooths from a GAM](man/figures/README-draw-gam-figure-1.png)

@@

    ![Model diagnostics figure](man/figures/README-appraise-figure-1.png)
